---
title: "QMM_Assignment_2"
author: "Vineeth Kadiyam"
date: "2024-09-22"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(lpSolve)
```

```{r}
A12 <- matrix(c(20,900,420,15,1200,360,12,750,300), nrow = 3, ncol = 3, byrow = TRUE)
colnames(A12) <-(c('Space_Req', 'Sales Forecast(PerDay)', 'Profit')) 
rownames(A12) <-(c('Large', 'Medium','Small'))
A12
```

```{r}
A12 = matrix(c(750,900,450), nrow = 3, ncol = 1, byrow = TRUE)
colnames(A12)=(c('Excess Capacity')) 
rownames(A12)=(c('Plantl', 'Plant2', 'Plant3')) 
A12
```

Let 
    L1, M1, S1 = Number of large, medium, and small units produced at Plant 1
    L2, M2, S2 = Number of large, medium, and small units produced at Plant 2
    L3, M3, S3 = Number of large, medium, and small units produced at Plant 3

The objective function is
    
    Max Z = 420(L1 + L2 + L3) + 360(M1 + M2 + M3) + 300(S1 + S2 + S3) 
    
Rearranging this, the objective becomes 
   
    Max Z = 420L1 + 360M1 + 300S1 + 420L2 + 360M2 + 300S2 + 420L3 + 360M3 + 300S3 
    
subject to the following constraints.,
 
 Production Capacity Constraints:    
     
     L1 + M1 + S1 ≤ 750
     L2 + M2 + S2 ≤ 900
     L3 + M3 + S3 ≤ 450
 
 Storage Space Constraints:     
     
     20L1 + 15M1 + 12S1 ≤ 13000
     20L2 + 15M2 + 12S2 ≤ 12000
     20L3 + 15M3 + 12S3 ≤ 5000
 
 Sales Forecast Constraints:   
     
     L1 + L2 + L3 ≤ 900
     M1 + M2 + M3 ≤ 1200
     S1 + S2 + S3 ≤ 750
     
 Capacity Usage Equality:
 
 (L1 + M1 + S1) ∗ (100/750) = (L2 + M2 + S2) ∗ (100/900) = (L3 + M3 + S3) ∗ (100/450)    
Non negativity constraints: 

         L1, L2, L3, M1, M2, M3, S1, S2, S3 ≥ 0
         
```{r}
#Objective Function
Object <- c(420, 360, 300, 420, 360, 300, 420, 360, 300)
```
         
```{r}
#Constraints

Cnstrants  <- matrix(c(
  
  # Production capacity
  1, 1, 1, 0, 0, 0, 0, 0, 0,  # Plant 1
  0, 0, 0, 1, 1, 1, 0, 0, 0,  # Plant 2
  0, 0, 0, 0, 0, 0, 1, 1, 1,  # Plant 3
  
  # Storage
  20, 15, 12, 0, 0, 0, 0, 0, 0,  # Plant 1
  0, 0, 0, 20, 15, 12, 0, 0, 0,  # Plant 2
  0, 0, 0, 0, 0, 0, 20, 15, 12,  # Plant 3
  
  # Sales forecast
  1, 0, 0, 1, 0, 0, 1, 0, 0,  # Large units
  0, 1, 0, 0, 1, 0, 0, 1, 0,  # Medium units
  0, 0, 1, 0, 0, 1, 0, 0, 1,  # Small units
  
  6, 6, 6, -5, -5, -5, 0, 0, 0,
  0, 0, 0, 1, 1, 1, -2, -2, -2,
  3, 3, 3, 0, 0, 0, -5, -5, -5
  
), nrow=12, byrow=TRUE)
Cnstrants
```

```{r}
#Define the constraint direction
Direct<-c("<=","<=","<=","<=","<=","<=","<=","<=","<=","=","=","=")
Direct
```

```{r}
# RHS of the constraints
RHS <- c(750, 900, 450, 13000, 12000, 5000, 900, 1200, 750, 0, 0, 0)
RHS
```
         
```{r}
#Solve the linear programming problem
linear_prog_result <-lp("max", Object, Cnstrants, Direct, RHS)
linear_prog_result
```
         
```{r}
#Values of decision variables
linear_prog_result$solution
```
         
         